---
title: "Visualizing simulator data"
author: "Martijn Tennekes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Visualizing simulator data}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
```

The simulator software is a framework to run mobile network data micro-simulations [1]

## Example data from the simulator

The example data is contained in this package as a zip file. It can be retrieved and extracted as follows.

```{r}
library(mobvis)
zipfile <- system.file("sim", "simdata.zip", package="mobvis")

dir <- "simdata"
if (!dir.exists(dir)) dir.create(dir, recursive = TRUE) else unlink(dir, recursive = TRUE)
unzip(zipfile, exdir = dir)
```

The input files are contained in the root folder (in this case `"simdata"`), and the output files in the `"output"` subfolder.

In order to use this simulator data in R, we have to create a list object.

```{r}
sim <- list(input_dir = "simdata",
            output_dir = "simdata/output",
            mno = "MNO1",
            crs = sf::st_crs("+proj=aeqd +lat_0=16.06 +lon_0=-22.85 +x_0=0 +y_0=0"))
```

Besides the input and output directories, it also contains a crs (coordinate reference system), which is needed to create interactive maps.
Since this data is fictional, the crs is centered on Boa Vista, a small island in the Atlantic Ocean.


## Signal strength

```{r, fig.show="hold", out.width="40%"}
rst <- sim_get_raster(sim)
cp <- sim_get_cellplan(sim)
region <- sim_get_region(sim)
strength <- sim_get_signal_strength(sim, rst, cp)

map_sig_strength(rst, dt = strength, cp = cp, region = region, cells = 3, type = "dBm", interactive = FALSE)
map_sig_strength(rst, dt = strength, cp = cp, region = region, cells = 3, type = "s", interactive = FALSE)
```


## Event location

The following function 

```{r}
param <- mobloc_param()
strength[, dist:= NA]
strength_llh <- create_strength_llh(strength, param = param)

settings = mobvis_settings()
settings$cell_colors["Normal cell"] <- "black"

map_pag(rst, dt = strength_llh, cp = cp, region = region, cells = 3, interactive = FALSE, settings = settings)

```


## 




## References

1. Reference

