---
title: "Visualizing simulator data"
author: "Martijn Tennekes"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Visualizing simulator data}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(mobvis)
knitr::opts_chunk$set(
    collapse = TRUE,
    fig.width=6, 
    fig.height=4,
    comment = "#>"
)
```

The simulator software is a framework to run mobile network data micro-simulations [1]

## Example data from the simulator

Example data for the simulator, both the input and the output files, are contained in this package as a single zip file. It can be retrieved and extracted as follows.

```{r}
# specify folder for the simulator files
dir <- "simdata"
if (!dir.exists(dir)) dir.create(dir, recursive = TRUE) else unlink(dir, recursive = TRUE)

# unzip the zip file into that folder 
zipfile <- system.file("sim", "simdata.zip", package = "mobvis")
unzip(zipfile, exdir = dir)
```

In this case, the files will be located in the `"simdata"` subfolder of the working directory. The input files are stored in that folder, and the output files in the subfolder `"simdata/output"`.

In order to use this simulator data in **mobvis**, we have to create a list object that contains a few settings.

```{r}
sim <- list(input_dir = "simdata",
            output_dir = "simdata/output",
            mno = "MNO1",
            crs = sf::st_crs("+proj=aeqd +lat_0=16.06 +lon_0=-22.85 +x_0=0 +y_0=0"))
```

Besides the input and output directories, it also contains the MNO name, in this case `"MNO1"`, and a CRS (coordinate reference system). The latter can be used to is needed to 

it also contains a crs (coordinate reference system), which is needed to create interactive maps.
Since this data is fictional, the crs is centered on Boa Vista, a small island in the Atlantic Ocean.


## Signal strength

```{r, fig.show="hold", out.width="80%"}
rst <- sim_get_raster(sim)
cp <- sim_get_cellplan(sim)
region <- sim_get_region(sim)
strength <- sim_get_signal_strength(sim, rst, cp)

map_sig_strength(rst, 
                 dt = strength, 
                 cp = cp, 
                 region = region, 
                 cells = 3, 
                 type = "dBm", 
                 interactive = FALSE, 
                 settings = mobvis_settings_static(cell_size = 1, cell_offset = 75,
                                                   cell_labels = TRUE))
map_sig_strength(rst, 
                 dt = strength, 
                 cp = cp, 
                 region = region, 
                 cells = 3, 
                 type = "s", 
                 interactive = FALSE, 
                 settings = mobvis_settings_static(cell_colors = "gold", 
                                                   cell_size = 1, 
                                                   cell_offset = 75,
                                                   cell_labels = TRUE, 
                                                   cell_label_color = "white"))
map_best_server(rst = rst,
                dt = strength,
                cp = cp,
                region = region,
                cells = 3,
                type = "bsm",
                interactive = FALSE,
                settings = mobvis_settings_static(cell_colors = "black", 
                                                  cell_size = 1, 
                                                  cell_offset = 75,
                                                  cell_labels = TRUE, 
                                                  cell_label_color = "black"))


```


## Event location

The following function visualizes the event location.

```{r}
# Calculate the event location (likelihood) probabilities using mobloc
library(mobloc)
param <- mobloc_param()
strength[, dist:= NA]
strength_llh <- create_strength_llh(strength, param = param)

# Edit the visualization settings
settings = mobvis_settings_static(cell_size = 2)
settings$cell_colors["Normal cell"] <- "black"
settings$titles["pag"] <- "Event location"

# Create the plot
map_pag(rst, 
        dt = strength_llh, 
        cp = cp, 
        region = region, 
        cells = 3, 
        interactive = FALSE, 
        settings = settings)
```





## References

1. To do: add reference simulator documentation 

